\documentclass[11pt]{res} % default is 10 pt
\usepackage{hyperref}
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document}

\name{Arash Rouhani} % the \\[12pt] adds a blank line after name

\address{{\bf } \begin{tabular}[t]{l l}
    \\ \href{mailto:arash.rouhani@gmail.com}{arash.rouhani@gmail.com}
  \end{tabular} }
\address{{\bf } \begin{tabular}[t]{l l}
    \\ \href{http://www.arashrouhani.com}{www.arashrouhani.com}
  \end{tabular} }

\begin{resume}

\section{TECHNOLOGIES}
   \begin{itemize}
   \item
     C++: 5+ years of experience writing using the \href{https://google.github.io/styleguide/cppguide.html}{Google C++ Style Guide}.
   \item 
     Python: Used throughout my career.
   \item
     Functional Programming: Used Haskell in \href{https://github.com/search?l=Haskell\&q=\%40Tarrasch\&type=Repositories}{open source projects}.
 \end{itemize}

\section{WORKING EXPERIENCE}
  \textbf{Google}, {\footnotesize Senior Software Engineer, October 2017 (ongoing)}, Zurich, Switzerland
\vspace{0.2in}
   \begin{itemize}
     \item Developing features at Google scale and driving projects to launch. Mentoring multiple FTEs.
     \item I've studied the technical design of multiple YouTube products.
 \end{itemize}

\textbf{VNG Corporation}, {\footnotesize Data Engineer, November 2015 to February 2017}, HCMC, Vietnam
\vspace{0.2in}
   \begin{itemize}
     \item NLP, writing data pipelines and guiding the big data architecture.
 \end{itemize}

\textbf{Spotify}, {\footnotesize Data Engineer, April 2014 to November 2015}, Stockholm, Sweden
\vspace{0.2in}
   \begin{itemize}
     \item Data platform development and support. In particular I used Luigi and Apache Crunch.
 \end{itemize}

Internships at \textbf{Meta} and \textbf{Spotify}. 5 tech internships in total.

\section{PROFESSIONAL QUALIFICATIONS}
   \begin{itemize} % \itemsep -2pt  % reduce space between items
   \item
     Main contributor to \href{https://github.com/spotify/luigi}{luigi}, a
     popular open source task orchestrator.
   \item Second best Swedish participant in
    Google Code Jam 2010 and TopCoder Open 2010.
   \item Won the national Informatics Olympiad 2009. Participated in IOI 2009 in Bulgaria.
   \item I use Linux and version control 
     on a daily basis and I have written many
     \href{https://github.com/search?q=\%40Tarrasch+zsh+OR+antigen\&type=Repositories\&ref=searchresults}{zsh shell plugins}.
   \item Graduate thesis on the Haskell compiler (\href{https://www.arashrouhani.com/papers.html}{description}, \href{https://www.arashrouhani.com/papers/master-thesis.pdf}{pdf}).
   % \item Maintaining a Jenkins CI server and webmastering my university's
   %   student website.
   % \item Been a supplemental instruction leader and teaching assistant in
   %   various courses.
   % \item Speaking four languages: Swedish, English, Farsi and (some) German.
 \end{itemize}

\section{EDUCATION}
 \begin{itemize} % \itemsep -2pt  % reduce space between items
   \item Master's degree in Algorithms, Languages and Logic from Chalmers
     ({\footnotesize August 2009 to April 2014})
   \item Graduate level exchange student at Georgia Tech
     ({\footnotesize August 2012 to May 2013})
   \item GPA of 4.67/5.00 and 3.87/4.00 respectively. More info on my website.
 \end{itemize}

\section{OTHER MERITS}

\begin{itemize} % \itemsep -2pt  % reduce space between items
  \item Organizing the \href{http://progolymp.se/}{informatics contest in Sweden}.
    I've authored about
    30 tasks (with solutions and input data) and traveled to Estonia (2010),
    Denmark (2011), Latvia (2012), Taiwan (2014), Kazakhstan (2015) and Norway (2017) as a
    team leader with the Swedish IOI team.
\end{itemize}

\end{resume}
\end{document}
